S1: Extended Derivations for `A Data Driven Framework for Patient-Specific Neural Field Modelling'

### 2010-06-25 ltx/PLoS/LaTeX_Manuscript.tex
edits to author summary
added author summary

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLoS ONE authors please skip this step. 
% Author Summary not valid for PLoS ONE submissions.   
\section*{Author Summary}

>>>>

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLoS ONE authors please skip this step. 
% Author Summary not valid for PLoS ONE submissions.   
\section*{Author Summary}
With recent advances in medical imaging techniques and computing power we are entering a new age of neuroscientific research, where the amount of patient specific information is becoming incredibly detailed. In order to make the best use of this information, patient specific mathematical models should should be formed. This is particularly poignant where considering poorly understood complex systems such as large scale dynamics of the human brain. In terms of brain dynamics, there currently exists a library of neural field models that provide a theoretical explanation of various phenomena associated with various cognitive states and disease. In this paper we have created a platform for creating a patient specific neural field model. Within this platform, we propose rules for designing experiments in order to acquire the data with sufficient information and the mathematical formula to create such a model.
